\textbf{Autoreduction - an automated data reduction system for beamline instruments at the ISIS Facility}

### 2018-07-17 Documentation/paper/paper.tex

\title{\textbf{Autoreduction - an automated data reduction system for beamline instruments at the ISIS Facility}}
\author{J. R. Corderoy, T. Gowland, L. Greenwood, M. Noble, D. Oram and A. J. Markvardsen \\
(code contributors)\\
ISIS Facility, Rutherford Appleton Laboratory\\
Email: someone with an STFC email account}
\date{23/09/2015}

@@

\subsection{Reduction scripts}\label{reduction-scripts}

@@

\subsection{Web app}\label{web-app}

@@

@@

There is then a second node which runs Red Hat Enterprise Linux 7\cite{rhel}. This node
manages the parts of the system which are common between front and backend. This includes:
the MySQL database, the ActiveMQ server and the EndOfRunMonitor. This node should have
all the parts of the system that wouldn't need to be replicated as part of a worker node.

The third and final node manages the parts of the system that could be replicated such that 
we can have multiple worker nodes active in order to split the load of autoreduction and speed
up the overall process. This node has the QueueProcessor and the AutoreductionProcessor installed
on it. At the moment, the production system only uses one of these nodes but as the usage of the 
system increases, so too will the load. It might then be sensible to have multiple worker nodes.

@@

The software written as part this project is not tied to a
particular operating system since it is written entirely in Python and Django.

@@

\begin{enumerate}
\item
  Expanding the system to accommodate greater volume of use -- this
  might involve accomodating more reduction workers, for example
\item
  Integrating other methods of monitoring or listening for new runs -- the current
  method of watching a file archive is specific to ISIS
\item
  Make the WebApp accessible from outside of the laboratory
\item
  Have selected reduced data automatically catalogued in ICAT 
\item
  Improving portability and deployability of the current software; the
  state database/webapp is currently somewhat nontrivial to deploy
\item 
  Having the worker node machine as a Docker \cite{docker} image for
  easier deployment
\end{enumerate}

In the longer term, the system may be extended to listen to live streams and begin
processing data as soon as it comes off beamlines rather then waiting for files 
to be written to disk.

@@

\bibitem{Docker}
	Docker,
	\emph{Docker},
	\url{https://www.docker.com/}

\bibitem{iis}
    Microsoft Corporation,
    \emph{IIS},
    \url{http://www.iis.net/}.

\bibitem{fcgi}
    \emph{FastCGI},
    \url{https://github.com/FastCGI-Archives/FastCGI.com}.

@@

\bibitem{source}
    \emph{Autoreduction repository},
    \url{https://github.com/mantidproject/autoreduce}.

>>>>

\title{\textbf{Autoreduction - an automated data reduction system for beamline instruments at the ISIS Facility}}
\author{J. R. Corderoy, T. Gowland, L. Greenwood, M. Noble, D. Oram, \\
	A. J. Markvardsen, J. Shears, E. Oram, D. Fairbrother and G. Christian \\
(code contributors)\\
ISIS Facility, Rutherford Appleton Laboratory\\
Email: someone with an STFC email account}
\date{23/09/2015}

@@

\subsection{Reduction Scripts}\label{reduction-scripts}

@@

\subsection{WebApp}\label{web-app}

@@

\begin{figure*}
	\centering\includegraphics[width=0.8\linewidth]{machine_layout.png}
	\caption{An image showing which services are installed on which machines}
	\label{fig:machine_layout}
\end{figure*}

@@

There is then a second node which runs Windows Server 2012 running on the same Hyper-V cluster. This node
manages the parts of the system which are common between front and backend. This includes:
the MySQL database, the ActiveMQ server and the EndOfRunMonitor. This node should have
all the parts of the system that wouldn't need to be replicated as part of a worker node.

The third and final node, running Red Hat Enterprise Linux 7\cite{rhel}, manages the parts of the system that could be replicated such that 
we can have multiple worker nodes active in order to split the load of autoreduction and speed
up the overall process. This node has the QueueProcessor and the AutoreductionProcessor installed
on it. At the moment, the production system only uses one of these nodes but as the usage of the 
system increases, so too will the load. It might then be sensible to have multiple worker nodes.

A diagram of the different parts of the system is shown in figure \ref{fig:machine_layout}

@@

The software written as part this project is not tied to a particular operating system since 
it is written entirely in Python. However there is one limitation, the EndOfRunMonitor
cannot be ran on Linux as a network mounted drive does not produce the required filesytem events.

@@

\begin{enumerate}
\item
  Expanding the system to accommodate greater volume of use -- this
  might involve accomodating more reduction workers, for example
\item
  Integrating other methods of monitoring or listening for new runs -- the current
  method of watching a file archive is specific to ISIS
\item
  Make the WebApp accessible from outside of the laboratory
\item
  Have selected reduced data automatically catalogued in ICAT 
\item
  Improving portability and deployability of the current software; the
  state database/webapp is currently somewhat nontrivial to deploy
\item 
  Having the worker node machine as a Docker \cite{docker} image for
  easier deployment

\end{enumerate}

In the longer term, the system may be extended to listen to live streams and begin
processing data as soon as it comes off beamlines rather then waiting for files 
to be written to disk. Also an API could be implemented to reduce the complexity of
the QueueProcessor and allow integration of autoreduction into other software \cite{autoreduction-api}.

@@

\bibitem{docker}
	Docker,
	\emph{Docker},
	\url{https://www.docker.com/}

@@

\bibitem{source}
    Autoreduction repository,
    \url{https://github.com/isisScientificComputing/autoreduce}.

\bibitem{autoreduction-api}
  Autoreduction API GitHub issue
  \url{https://github.com/ISISScientificComputing/autoreduce/issues/73}.
